---
title: "How to Use OrbitR"
author: "Sarah Boukernafa"
date: "2024-04-24"
output: html_document
---

# Introduction

### Welcome! The OrbitR package provides basic tools for illustrating and calculating celestial mechanics in R. Is designed to be educational, introducing users to the concepts of orbits, planetary information, and simple astronomical calculations using R!

## Installation

### You can install the development version of OrbitR from GitHub using the following code:

```{r setup, include=TRUE}

# install.packages("devtools")  #Uncomment this line if devtools is not installed

# devtools::install_github("DissidiaTime/OrbitR")

```

## Loading the Package

### Once installed, you can load the package using:

```{r}

library(OrbitR)

```

## Functions Overview

### OrbitR includes several functions to help users understand basic celestial mechanics:

    get_planet_info(): Retrieves information about a specific planet.
    plot_orbit_simple(): Visualizes a simple circular orbit for a given planet.
    get_planet_position(): Calculates the current position of a planet in its orbit.
    simulate_orbit_adjustments(): Simulates changes to a planet's orbit based on adjustments to its velocity.

## Getting Planet Information

### The get_planet_info function provides basic data about planets in our solar system. Here's how to use it:

```{r}
mars_info <- get_planet_info("Mars")
print(mars_info)

```

## Plotting a Simple Orbit

### To show the concept of orbits, plot_orbit_simple creates a simple circular plot which is representing of an orbit of a planet of your choice:
```{r}

# Plots an orbit with of any hcosen planet:
plot_orbit_simple("Mars)

```

## Calculating Planet Position

### To calculate and print the current position of Mars in its orbit:
```{r}

# Calculate and plot Mars' position
mars_position <- get_planet_position("Mars")
print(mars_position)

```

## Simulating Orbit Adjustments

### Used to explore hypothetical changes in a planet's orbit caused by altering its velocity. Here's how to simulate an increase in Mars' velocity by 10%:
```{r}

# After loading the planets dataset
adjusted_orbit <- simulate_orbit_adjustments(planets, "Mars", 1.1)
print(adjusted_orbit)

```

## Example Use Case

### Now lets use all the functions to visualize the data and orbit of Earth!:

```{r}

# Step 1: Load the Package

# Ensure that the OrbitR package is loaded

# Retrieve Earth data
earth_info <- get_planet_info("Earth")
print(earth_info)

# Simulate a 10% increase in Earth's orbital velocity and observe the changes in orbital distanc!
adjusted_earth_orbit <- simulate_orbit_adjustments(earth_info, "Earth", 1.1)
print(adjusted_earth_orbit)

```

# Enjoy!

### OrbitR serves as an introductory tool for understanding and visualizing basic concepts in celestial mechanics using R. It is suitable for educational purposes and works well in helping users learn about planetary data, orbits, and the application of Kepler's laws in a basic straightforward manner.
